---
title: "Using Multidimensional RQA in the lorenz system"
output: html_notebook
---

## Info on the project
Looking into the output of the multidimensional RQA function from the following reference:

Wallot, S., & Leonardi, G. (2018). Analyzing Multivariate Dynamics Using Cross-Recurrence Quantification Analysis (CRQA), Diagonal-Cross-Recurrence Profiles (DCRP), and Multidimensional Recurrence Quantification Analysis (MdRQA) – A Tutorial in R. Frontiers in Psychology, 9.

### Read in the necessary libraries

```{r message=FALSE, echo=TRUE}
#load in necessary libraries
library(ggplot2)
library(casnet)
library(nonlinearTseries)
library(igraph)

source(file = "mdrqa.R")
```


```{r message=FALSE, echo=TRUE}
sessionInfo()
```

```{r}
lor_df <- data.frame(lorenz(time=seq(0,30,by = 0.05), do.plot = FALSE))
```

```{r}
plot.ts(lor_df$x)
plot.ts(lor_df$y)
plot.ts(lor_df$z)
```

```{r}
rgl::plot3d(x=lor_df$x, y=lor_df$y, z=lor_df$z, type="l", col = rainbow(1000))
```


```{r}
# lor_mdrqa <- mdrqa(data = lor_df, emb=1, del=1, rad = 0.05, norm="euc")
```

```{r}
lor_mdrqa <- mdrqa(data = as.matrix(lor_df$x, lor_df$y, lor_df$z), emb = 1, del = 1, norm = "euc", rad = 0.2) # run MdRQA3 on the x, y and z dimensions of the Lorenz system

image(lor_mdrqa$RP) # show recurrence plot
```
```{r}
emDim = 1
emLag = 1
emRad = 0.2

tmp <- lor_df[c("x", "y", "z")]

RNs <- plyr::llply(1:3, function(r) rn(y1 = tmp[,r], emDim = emDim, emLag = emLag, emRad = emRad, targetValue = 0.05))
```

```{r}
layers <- plyr::llply(RNs, function(r) igraph::graph_from_adjacency_matrix(r, mode="undirected", diag = FALSE))
names(layers) <- colnames(tmp)
```

```{r}
mrn_summary <- mrn(layers = layers)
mrn_summary$meanValues
```


```{r, fig.width = 7, fig.height = 7}
edge_weights_RNNs_mat <- mrn_plot(layers = layers, RNnodes = TRUE)
edge_weights_RNNs_mat$MRN
```

```{r, fig.width = 7, fig.height = 7}
edge_weights_mat <- mrn_plot(layers = layers, RNnodes = FALSE, doSave = FALSE, showVertexLegend = TRUE)
edge_weights_mat$MRN
```

